Paper figures

### 2020-10-05 notebooks/paper_plots_0909.Rmd
scatter plots of random and real networks created.

pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))

combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
```

```{r}
p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
lgn = cowplot::get_legend(p2)
fig3 = plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
```

@@

combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
    bind_rows(
    data.frame(sens_deg_spearman= c(cor(pcc_df$deg, pcc_df$sens,method='spearman'),cor(yuri_df$deg,yuri_df$sens,method='spearman'),cor(huri_df$deg,huri_df$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df$deg, pcc_df$eff),cor(yuri_df$deg,yuri_df$eff),cor(huri_df$deg,huri_df$eff)), type='real',data=c('pcc','yuri','huri')))%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

p3 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real networks'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=3, labels=c('A','B','','C','D',''), rel_heights = c(0.45,0.45,0.1))
ggsave('reports/figures/paper_figures_0916/fig2.png',width=7)
```

>>>>

pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
    py$e_pcc$e_list[[1]]$df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'random')
)%>%mutate(group=fct_relevel(group, c('real','random')))
yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
    py$e_yuri$e_list[[1]]$df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'random')
)%>%mutate(group=fct_relevel(group, c('real','random')))
huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
    py$e_huri$e_list[[1]]$df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'random')
)%>%mutate(group=fct_relevel(group, c('real','random')))
combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
```

```{r}
pcc_deg_eff = pcc_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
    facet_grid(rows = vars(group), scales='free') +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
pcc_deg_sens = pcc_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
    facet_grid(rows = vars(group), scales='free') +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
yuri_deg_eff = yuri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
    facet_grid(rows = vars(group), scales='free') +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
yuri_deg_sens = yuri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
    facet_grid(rows = vars(group), scales='free') +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
huri_deg_eff = huri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
    facet_grid(rows = vars(group), scales='free') +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
huri_deg_sens = huri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
    facet_grid(rows = vars(group), scales='free') +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
                   yuri_deg_eff, yuri_deg_sens,
                   huri_deg_eff, huri_deg_sens,
                   ncol=2)
ggsave('tmp.png',width=10,height=10)

p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
lgn = cowplot::get_legend(p2)
fig3 = plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
```

@@

combined_rewire_df <- rewire_df%>%select(data, eff_deg_spearman,sens_deg_spearman)%>%mutate(type = 'random')%>% 
    bind_rows(
    data.frame(sens_deg_spearman= c(cor(pcc_df$deg, pcc_df$sens,method='spearman'),cor(yuri_df$deg,yuri_df$sens,method='spearman'),cor(huri_df$deg,huri_df$sens,method='spearman')), eff_deg_spearman= c(cor(pcc_df$deg, pcc_df$eff,method='spearman'),cor(yuri_df$deg,yuri_df$eff,method='spearman'),cor(huri_df$deg,huri_df$eff,method='spearman')), type='real',data=c('pcc','yuri','huri')))%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

p3 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_spearman,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real networks'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=3, labels=c('A','B','','C','D',''), rel_heights = c(0.45,0.45,0.1))
ggsave('reports/figures/paper_figures_0916/fig2.png',width=7)
```
